Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
typos

@@

Climate data is usually large: many locations in space, and many points in time. This makes climate data challenging to work with computationally and to visualize. Plotting the raw data often reveals little more than a well-known observation that ``temperature is quite varied!'' Careful use of models than Careful use of models to decompose data into long-term trend, seasonal effects and error is vital for to make the problem both computationally and visually tractable.

>>>>

% Remove words like "obvious", "challenge", "scratched the surface"
% Make data URLs references

@@

Climate data is usually large: many locations in space, and many points in time. This makes climate data challenging to work with computationally and to visualize. Plotting the raw data often reveals little more than a well-known observation that ``temperature is quite varied!'' Careful use of models to decompose data into long-term trend, seasonal effects and error is vital for to make the problem both computationally and visually tractable.
